% LaTeX resume using res.cls

\documentclass[margin]{res}

\usepackage{hyperref}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft2.3\hoffset\centerline{\huge\bf Tingting Yu}

% Email: \url{tingting.yu@stat.ubc.ca}\\
Email: \url{yue.live520@gmail.com}\\
Web:\quad \url{http://oliviayu.github.io/}\\
% Mailing address: Department of Statistics, University of British Columbia,\\ 
% 3182 Earth Sciences Building,
% 2207 Main Mall,
% Vancouver, BC, Canada, V6T 1Z4 
Mailing address: Högalidsgatan 27, lgh 1104, 117 30 Stockholm, Sweden


% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip


\begin{resume}
 
%\section{CONTACT INFORMATION} 

%\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

\section{EDUCATION} {\bf Ph.D. in Statistics,} \\
                University of British Columbia, Vancouver, BC, Canada, \\ 
                2013 - In progress \\
                \\
				{\bf M.Sc. in Statistics,} \\
                University of British Columbia, Vancouver, BC, Canada, \\
                2011 - 2013 \\
                \\
				{\bf B.Sc. in Statistics,} \\
                Zhejiang University of Finance and Economics, Hangzhou, Zhejiang, China, \\
                2007 - 2011 \\

\section{RESEARCH INTERESTS} 
\begin{itemize}
    \item Joint modelling;
    % \item Machine learning;
    \item Longitudinal and survival data analysis;
    \item Missing data, measurement errors, censoring data, outliers;
    \item Cancer and HIV/AIDS studies.
\end{itemize}
			
    % - Joint models\\
    % - Longitudinal data analysis\\
    % - Survival analysis\\
    % - Missing data, outliers, measurement errors\\
    % - Correlated data\\
    % - Cancer and HIV/AIDS research\\
 

% \section{LANGUAGES \\ \& SOFTWARES} R, LaTeX, Sublime 
 
\section{ACADEMIC/WORKING EXPERIENCES} 

\vspace{30pt}

{\sl Data Scientist/Researcher}, Ecoation Innovative Solutions Inc \hfill Jan 2018 - Current 

{\sl Research Assistant}, UBC \hfill May 2012 - Current 
                %  \begin{itemize}  \itemsep -2pt %reduce space between items
                %  \item supervisor: Prof. Lang Wu
                % \end{itemize}

{\sl Statistical Consultant}, Short Term Consulting Service, UBC
\hfill May 2012 - Aug 2017

{\sl Research Assistant}, Fred Hutchinson Cancer Research Center 
                 \hfill Sep 2014 - July 2017 


{\sl Data Analyst}, BC Cancer Research Center
                 \hfill Dec 2016 - Jun 2017 
                

{\sl Teaching Assistant}, UBC \hfill Jan 2012 - Apr 2017 \\
                STAT 241/251: Introductory Probability and Statistics/Elementary Statistics, \\
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item head TA, Jan 2013 - Apr 2017
                 \item held labs and TA office hours
                 \item helped with making lab materials, Jan 2015-May 2015
                 \item helped with making lecture notes, Jul 2012-Dec 2012                 
                \end{itemize}
 
 {\sl Teaching Assistant}, UBC \hfill Sep 2011 - Dec 2011 \\
                STAT 200: Elementary Statistics for Applications, 
                \begin{itemize} \itemsep -2pt %
                    \item held labs and TA office hours
                \end{itemize}

\section{Volunteer Experience}              

{\sl Short Term Consulting Service Manager}, UBC \hfill Feb 2017 - Aug 2017  


{\sl Graduate student seminar organizer}, UBC \hfill Sep 2015 - Apr 2016
                 % Statistics department, 
                 % UBC, Vancouver, BC 
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                  \item organized weekly graduate student seminar
                 % \item Organizing student seminar lecture series on parallel
                 % computing in R
                 \item organized student seminar lecture series on statistical
                 analysis of network data
                \end{itemize}                


\section{PUBLICATIONS} % (fold)
T.T. Yu, L. Wu, and P.B. Gilbert (2018). Robust joint modelling of mixed and truncated longitudinal data  and survival data. {\em under preparation}.

T.T. Yu, L. Wu, and P.B. Gilbert (2018). New Approaches for Censored Longitudinal Data in Joint Modelling of Longitudinal and Survival Data, with Application to HIV Vaccine Studies. {\em under revision}.

T.T. Yu, L. Wu, and P.B. Gilbert (2017). A joint model for mixed and truncated longitudinal data and survival data, with application to HIV vaccine studies. {\em Biostatistics}. 

T.T. Yu and L. Wu (2016). Robust Modelling of the Relationship Between CD4 and Viral Load for Complex AIDS Data. {\em Journal of Applied Statistics}.

Y. Cheng, L. Wu, C. Lum, J. Zidek, and T.T. Yu (2016).  Wood Property Relationships and Survival Models in Reliability. {\em Applied Stochastic Models in Business and Industry}.

L. Wu and T.T. Yu (2016).  Joint Modeling of Longitudinal and Survival Data. {\em Wiley StatsRef: Statistics Reference Online}.


\section{TALKS \&  PRESENTATIONS}  

{\it A joint model for mixed and censored longitudinal data and survival data, with application to HIV vaccine studies}, 
Winter 2016 SFU/UBC Joint Seminar, March 2016.

{\it Jointly Modeling Longitudinal Process with Measurement Errors, Missing Data, and Outliers},
Statistical Society of Canada Annual Meeting, University of Toronto, May 2014.

{\it Causal effect of economic recession on TV viewing and video game playing in the last decade in the United States}, Statistical Society of Canada Annual Meeting, University of Toronto, May 2014.



\section{HONOURS \&  AWARDS}
 2014 SSC Travel Award

 2013-17 Faculty of Science Graduate Award (Ph.D.)

 2011-13 Faculty of Science Graduate Award (M.sc.)

 2007-2010 Second Prize of Excellent Undergraduate Scholarship 

 2009 Second Prize in Zhejiang Contest District in China Undergraduate Mathematical Contest in Modeling

 2009 Zhejiang Province Undergraduate Statistical Research Competition Winner

  2009/2008 Second/Third Prize in Zhejiang Province Collegiate Advanced Mathematics (Calculus)
Contest in China


\end{resume}
\end{document}

